Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-31 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Updated 4 cut results to only go up to 85% wires cut, since we had trouble at 90%
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4571 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
fixing the text to be consistent with the terms in the equations. Ehsan: done with my edits. what's left to do is just proofreading the whole paper.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4572 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\subsection{Virtex-7 Interposer-based FPGAs}
\label{virtex7section}

@@

where 
\setlength{\arraycolsep}{0.0em}
\begin{equation}
\label{eq:cprime}
C' = \frac{ratio\_wires\_cut}{avg\_chany\_W(n)}
\end{equation}
\setlength{\arraycolsep}{5pt}

\textit{bbHeight(n)} is the height of the bounding box of the net \textit{n} and $ratio\_wires\_cut$ is the ratio of wires cut at the cutline. This formulation of $C'$ ensures that the new cost term is of roughly the same magnitude as $wire\_cost_{orig}$ in (\ref{eq:bbcost}) and that it is weighted more heavily for interposer architectures in which the wiring between dice is more scarce.

This cost function performs better than several others as shown in \cite{interposer2014}, and we believe the key to the good performance of this cost functions is that \textit{cut\_cost} produces gradual gains as bounding boxes crossing the cutline shrink to be closer and closer to being captured entirely on one side of the cutline. Consider for example the 3 bounding boxes shown in Figure \ref{fig:bb_illustration}. Note that bounding box (a) and (b) both cross the cutline, but (b) is penalized less by (\ref{eq:cost2}) because bounding box (b) is mostly on the lower side of the cutline; it is more likely that later placement changes will result in the bounding box moving entirely below the cutline, reducing interposer wiring demand. Cost function (\ref{eq:cost2}) penalizes bounding box (a) more than (b) and (b) more than (c) to guide placement to gradually move bounding boxes to one side or the other of a cutline.

@@

The optimizations also guide the placer to keep related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. This speed improvement is fairly consistent across a wide range of \% wires cut, averaging 12.5\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_fmax}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{wires_cut_4part}
\caption{Impact of number of dice on routability. TODO JAVEED -- LU32 90\% result is missing}
\label{fig:wires_cut_4part}
\end{figure}

Systems with more dice are slower; on average the critical path delay is xx\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay. TODO JAVEED -- LU32 90\% result is missing}
\label{fig:crit_path_4part}
\end{figure}

>>>>

\subsection{Virtex Interposer-based FPGAs}
\label{virtex7section}

@@

where 
\setlength{\arraycolsep}{0.0em}
\begin{equation}
\label{eq:cprime}
C' = \frac{ratio\_wires\_cut}{W_{chany}}
\end{equation}
\setlength{\arraycolsep}{5pt}

\textit{bbHeight(n)} is the height of the bounding box of the net \textit{n} and $ratio\_wires\_cut$ is the ratio of wires cut at the cutline. This formulation of $C'$ ensures that the new cost term is of roughly the same magnitude as $Cost_{W\_orig}$ in (\ref{eq:bbcost}) and that it is weighted more heavily for interposer architectures in which the wiring between dice is more scarce.

This cost function performs better than several others as shown in \cite{interposer2014}, and we believe the key to the good performance of this cost functions is that $Cost_{cut}$ produces gradual gains as bounding boxes crossing the cutline shrink to be closer and closer to being captured entirely on one side of the cutline. Consider for example the 3 bounding boxes shown in Figure \ref{fig:bb_illustration}. Note that bounding box (a) and (b) both cross the cutline, but (b) is penalized less by (\ref{eq:cost2}) because bounding box (b) is mostly on the lower side of the cutline; it is more likely that later placement changes will result in the bounding box moving entirely below the cutline, reducing interposer wiring demand. Cost function (\ref{eq:cost2}) penalizes bounding box (a) more than (b) and (b) more than (c) to guide placement to gradually move bounding boxes to one side or the other of a cutline.

@@

The optimizations also guide the placer to keep related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. This speed improvement is fairly consistent across a wide range of \%~wires~cut, averaging 12.5\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_fmax}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\input{wires_cut_4part}
\caption{Impact of number of dice on routability.}
\label{fig:wires_cut_4part}
\end{figure}

Systems with more dice are slower; on average the critical path delay is xx\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay.}
\label{fig:crit_path_4part}
\end{figure}
